### 2020-10-22 thesis/chap_2.tex
explain base map, comment 17
comment 18

We employed a method coined “consensual participatory mapping in geographically structured focus groups”. Participants whose organisations operate in the same region (the same MRC) were seated at the same table. See table \ref{tab:workshoptables} for the breakdown of each MRC by table. In addition, for participants whose zone of influence or zone of action covered the whole region, two “regional tables” were created. In the subsequent sections, the workshop results are divided between the regional and regional tables.
The general method proceeded in 3 exercises, each step involving the same focus groups.

@@

To ensure that this system is used consistently throughout the workshop, each participant was given a personal folder with their own color-coded stickers and post-its. Participants were instructed to only use the stickers and material that have been personally handed to them. All participants were given a visual aid to remind them of the agenda of the workshop. Facilitators were also present at almost every table and helped facilitate the discussion. They were given a document to help them in this role. The workshop materials, including the ethics approval document for this research project can be found in Appendix 2.\\

>>>>

We employed a method coined “consensual participatory mapping in geographically structured focus groups”. Participants whose organisations operate in the same region (the same MRC) were seated at the same table. See table \ref{tab:workshoptables} for the breakdown of each MRC by table. In addition, for participants whose zone of influence or zone of action covered the whole region, two “regional tables” were created. In the subsequent sections, the workshop results are divided between the regional and regional tables. The base map used in the exercises is the same as used in figures \ref{fig:trans_AC} and \ref{fig:reg_AC} (Chapter 1 land use map, 2010). 
The general method proceeded in 3 exercises, each step involving the same focus groups.

@@

To ensure that this system is used consistently throughout the workshop, each participant was given a personal folder with their own color-coded stickers and post-its. Participants were instructed to only use the stickers and material that have been personally handed to them. All participants were given a visual aid to remind them of the agenda of the workshop. Facilitators were also present at almost every table and helped facilitate the discussion (faciltators were either affiliated to McGill University or to the RMN, and one of them was an independent contractor and workshop professional). They were given a document to help them in this role. The workshop materials, including the ethics approval document for this research project can be found in Appendix 2.\\
